### 2015-03-01 paper/paper.tex
stuff

Let us demonstrate this with a small example.
We have a set of variables describing properties of people: \texttt{is\_under\_18},
\texttt{has\_driving\_licence} and \texttt{is\_drunk}.

% For instance, the following constraints describe rules for driving a car.
% \begin{verbatim}
% can_drive
% has_driving_licence
% is_under_18
% is_drunk
% \end{verbatim}

% Next, we represent a possible situation in the world. In order to be allowed to drive, a person must have a driving licence and they must not be drunk. This is represented by the clause $can\_drive ∧\wedge has\_driving\_licence ∧\wedge \neg is\_drunk$. Furthermore, from the world knowledge, we know that in order to have a driving licence, one must be over 18. This is represented by the second clause.

Clause 1 describes a possible situation in a world: someone is behaving in away that makes you think of a hypothesis ``either they are underage or
drunk''. This is represented as \texttt{is\_under\_18} $\vee$
\texttt{is\_drunk}. Just by this clause we can't solve the reason for the
behaviour: it can be one of them or both.

Clause 2 comes from the world knowledge that in order to have a
driving licence, one must be over 18. The form of the clause is
obtained by applying negation distributively over the more intuitive
clause $\neg$ (\texttt{has\_driving\_licence} $\wedge$
\texttt{is\_under\_18}): it is not possible to both have driving
licence and be under 18.

\begin{enumerate}
\item \texttt{is\_under\_18} $\vee$ \texttt{is\_drunk}
\item ($\neg$ \texttt{has\_driving\_licence}) $\vee$ ($\neg$ \texttt{is\_under\_18})
\item \texttt{has\_driving\_licence}
\end{enumerate}

Clause 3 provides us some undeniable evidence that
the person has a driving licence. By this clause, 
we know that the variable \texttt{is\_under\_18} is not true.
Knowing that, we can eliminate \texttt{is\_under\_18} from the first
clause. 
The solution is below: the three variables must have these values in order to
satisfy the constraints.

\begin{itemize}
\item \texttt{is\_drunk} = True
\item \texttt{is\_under\_18} = False
\item \texttt{has\_driving\_licence} = True
\end{itemize}

SAT solving is used for many applications where constraints must be
satisfied, such as software and hardware verification.

@@

\begin{lstlisting}
((1,[Lem "the",Det]),Var 1)
((2,[Lem "bear",N,Sg]),Var 2)
((2,[Lem "bear",V,Pl]),Var 3)
((3,[Lem "sleep",N,Pl]),Var 4)
((3,[Lem "sleep",V,Sg]),Var 5)
((4,[Lem "in",Prep]),Var 6)
((4,[Lem "in",Adv]),Var 7)
((5,[Lem "the",Det]),Var 8)
((6,[Lem "house",V,Inf]),Var 9)
((6,[Lem "house",N,Sg]),Var 10)
\end{lstlisting}

@@

Another property of CG is that cannot remove all readings: if all
other analyses are eliminated, the remaining analysis must be
returned, even if it were to be eliminated at the next pass. 
However, this property isn't implemented in the SAT version.

@@

We could also express the rules like this:
\begin{lstlisting}
rmPlIfSg = Remove [Pl] (NOT (C (Exactly (-1)) [Pl]))
rmSgIfPl = Remove [Sg] (NOT (C (Exactly (-1)) [Sg]))
\end{lstlisting}

@@

data Condition = C Position [Tag]
               | NOT Condition
               | AND Condition Condition
               | OR  Condition Condition 
\end{lstlisting}

The data type for Rule is either remove or select a list of tags, with condition(s).
For Condition, there are basic conditions (position and a list of context tags) and combined conditions, with constructors `NOT', `AND' and `OR'. For instance, the following rule is read as ``remove tag for any verb, if the lemma is \emph{bear} or there is a determiner or an article anywhere to the left''.

>>>>

SAT solving is used for many applications where constraints must be
satisfied, such as software and hardware verification.
Application of logic to POS tagging or shallow parsing isn't new;
\cite{lager1998, lager2000} presents POS tagging rules as logic, and uses
a theorem prover (DisLog, TODO cite) to implement small constraint rules.
Inspired by the approach, my implementation tries to emulate the CG
formalism in behaviour and features offered.

@@

\begin{lstlisting}
((1,["the",<det>]),Lit v0)
((2,["bear",<n>,<sg>]),Lit v1)
((2,["bear",<vblex>,<pl>]),Lit v2)
((2,["bear",<vblex>,<fin>]),Lit v3)
((3,["sleep",<n>,<pl>]),Lit v4)
((3,["sleep",<vblex>,<sg>,<p3>]),Lit v5)
\end{lstlisting}

@@

Another property of CG is that cannot remove all readings: if all
other analyses are eliminated, the remaining analysis must be
returned, even if it were to be eliminated at the next pass. 
This is implemented as a clause that says that at least one literal
of each position must be true.

@@

We could also express the rules like this:
\begin{lstlisting}
rmPlIfSg = Remove [Pl] (C (Exactly (-1)) (False,[Pl]))
rmSgIfPl = Remove [Sg] (C (Exactly (-1)) (False,[Sg]))
\end{lstlisting}

@@

data Condition = C Position (Bool,[Tag])
               | AND Condition Condition
               | OR  Condition Condition 
\end{lstlisting}

The data type for Rule is either remove or select a list of tags, with condition(s).
For Condition, there are basic conditions (position and a list of context tags) and combined conditions, with constructors `AND' and `OR'. For instance, the following rule is read as ``remove tag for any verb, if the lemma is \emph{bear} or there is a determiner or an article anywhere to the left''.
